Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2016-11-21 R0V0.tex
Change the formulation of Problem 1. Add pargraph I.22 to explain that the controller can have a different topology than then plant.

@@

\mypara Let $N>0$ be an integer, for each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}.

@@

\begin{problem}\label{problem formulation}
	For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}. Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into the set $\mathscr{K}(i)\subset\mathbb{N}_{[1,N]}$.
\end{problem}

@@

\begin{definition}\label{def:}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if for fixed controls $u$ and $\delta u$ for systems \eqref{eq:general system} and \eqref{eq:general system:differential}, respectively, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta_x,u,\delta_u))\leq -\lambda V(x,\delta_x)
 	 	 \end{equation}
 	 	 holds, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

@@

\section{Distributed Design of Decentralized Controllers}

@@

\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stability of the origin, for some classes of systems.

>>>>

\usepackage{enumerate}

@@

\mypara Let $N>0$ be an integer, for each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}. Using this decomposition, the interconnection of system~\eqref{eq:general system} is described by the graph $\mathscr{G}=(\mathscr{V},\mathscr{E})$.

@@

\begin{problem}\label{problem formulation}
	\begin{enumerate}[{P}$_1$.]\hfill
		\item For any forward complete solution $X^\ast(\cdot,x^\ast,u^\ast)$, find a feedback law $k^\ast$ such that, for every initial condition $x\in\mathbb{R}^n$, the issuing solution to  \eqref{eq:general system} in closed loop satisfies the inequality~\eqref{eq:global exponential uniform stabilizability}. Moreover, for each index $i\in\mathbb{N}_{[1,N]}$, the $i$-th component $k^\ast$ depends on specific components of $x$ that are collected into a set $\mathscr{K}(i)$ of graph nodes;

		\item Given a graph $\mathscr{G}_c=(\mathscr{V}_c,\mathscr{E}_c)$ describing the communication network among the components of the controller, the set $\mathscr{K}(i)$ is composed of elements from $\mathscr{E}_c$.
	\end{enumerate}
\end{problem}

\mypara In other words, item P$_1$ of Problem~\ref{problem formulation} states that the controller is decomposed into smaller components. Each of these depends on the states  prescribed by the set $\mathscr{K}$. Item P$_2$ of Problem~\ref{problem formulation} states that this set may not necessarily correspond to the states which system~\eqref{eq:subsystem} depends on. This item addresses the case in which there exists a difference between the communication topology of the network represented by Equation~\eqref{eq:general system} and the communication topology of the distributed controller.

@@

\begin{definition}\label{def:}
		 A metric $V:\mathbb{R}^n\times\mathbb{R}^n\to\mathbb{R}_{\geq0}$ receives the adjective \emph{contraction} if, for fixed controls $u\equiv0$ and $\delta_u\equiv0$ for systems~\eqref{eq:general system} and \eqref{eq:general system:differential}, there exists a value $\lambda>0$ such that the inequality
	 	 \begin{equation}
	 	 	\tfrac{dV}{dt}(X(t,x,u),\Delta(t,x,\delta_x,0,0))\leq -\lambda V(x,\delta_x)
 	 	 \end{equation}
 	 	 holds, for every pair $(x,\delta_x)\in\mathbb{R}^n\times\mathbb{R}^n$.
\end{definition}

@@

\section{Distributed Design of Distributed Controllers}

@@

\mypara Although the requirement of a sum-separable structure seems to be restrictive, this structure is equivalent to the (possibly local) stabilizability of the origin, for some classes of systems.
